method

### 2022-06-09 06_Paper/ER-ED/method.Rmd
removed one sentence

Young healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE*[@Greiner2015] at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
In the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
Then, they will complete an effort discounting (ED) procedure regarding the n-back levels on screen, followed by a random repetition of one n-back level.
The second session will take place exactly one week after session one.
Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training will ensure that all participants are able to implement the ER strategies.
Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted, followed by an ED procedure regarding the ER strategies.
After that, participants will choose one ER strategy to repeat one more time.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].

@@

*Part two: ER effort discounting.* <br> In the second part, ER effort discounting will take place.
The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.[-@Westbrook2013] with a major change.
We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), each of the two strategies will be presented with a monetary reward.
The order of the pairings will be randomized.
Because there is no strategy that is objectively more difficult, we will add initial comparisons asking the participants to choose between "1 € for strategy A or 1 € for strategy B".
They decide by clicking the on-screen button of the respective option.
Each of the three strategy pairs will be presented three times in total, in a randomized order and randomly assigned which strategy appears on the left or right side of the screen.
For each pair, the strategy that was chosen at least two out of three times will be assigned the flexible starting value of 1 €, the other strategy will be assigned the fixed value of 2 €.
After this, comparisons between strategies will follow the original COG-ED paradigm[@Westbrook2013].
Each pairing is presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € is either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
The adjustment starts at 0.50 € and each is half the adjustment of the previous step, rounded to two digits after the decimal point.
If a participant always chooses the strategy with the fixed 2 € reward, the other strategy's last value on display will be 1.97 €, if they always choose the lower strategy, its last value will be 0.03 €.
The sixth adjustment of 0.02 € will be done during data analysis, based on the participants' decision in the last display of the pairing.
Participants will be instructed to decide as realistically as possible by imagining that the monetary reward is actually available for choice.

@@

Data collection and analysis will not be performed blind to the conditions of the experiments.
Data of whole participants will be excluded from analysis if participants withdraw their consent or they state that they did not follow experimental instructions.
EMG data of subjects will be excluded from analysis if errors occured during recording.
No further data exclusions are planned.
The level of significance will be set to $\alpha=.05$.
For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the *afex* package[@Singmann2021].
Greenhouse-Geisser-corrected degrees of freedom and associated $p$-values and will be reported when the assumption of sphericity is violated.
If the within-subjects factor of interest is significant, pairwise contrasts will be calculated using Bonferroni adjustment for multiple testing.
Proportion of explained variance $\eta_{p}^{2}$ will be reported as a measure of effect size.

@@

*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.02 € will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
Second, the resulting monetary value will be divided by 2.00 € to arrive at the SV of the opposite strategy in each pairing.
Therefore, the SVs of the flexible strategies are 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they are the preferred strategy of each pairing.
The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing. 
The final SV per strategy for each participant will be computed by averaging the SVs of each strategy across pairings.

>>>>

Young healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE*[@Greiner2015] at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
In the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
Then, they will complete an effort discounting (ED) procedure regarding the n-back levels on screen, followed by a random repetition of one n-back level.
The second session will take place exactly one week after session one.
Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training will ensure that all participants are able to implement the ER strategies.
Next, electrodes to measure facial EMG will be attached and the ER task will be conducted, followed by an ED procedure regarding the ER strategies.
After that, participants will choose one ER strategy to repeat one more time.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].

@@

*Part two: ER effort discounting.* <br> In the second part, ER effort discounting will take place.
The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.[-@Westbrook2013] with a major change.
We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), each of the two strategies will be presented with a monetary reward.
Because there is no strategy that is objectively more difficult, we will add initial comparisons asking the participants to choose between "1 € for strategy A or 1 € for strategy B".
They decide by clicking the on-screen button of the respective option.
Each of the three strategy pairs will be presented three times in total, in a randomized order and randomly assigned which strategy appears on the left or right side of the screen.
For each pair, the strategy that was chosen at least two out of three times will be assigned the flexible starting value of 1 €, the other strategy will be assigned the fixed value of 2 €.
After this, comparisons between strategies will follow the original COG-ED paradigm[@Westbrook2013].
Each pairing is presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € is either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
The adjustment starts at 0.50 € and each is half the adjustment of the previous step, rounded to two digits after the decimal point.
If a participant always chooses the strategy with the fixed 2 € reward, the other strategy's last value on display will be 1.97 €, if they always choose the lower strategy, its last value will be 0.03 €.
The sixth adjustment of 0.02 € will be done during data analysis, based on the participants' decision in the last display of the pairing.
Participants will be instructed to decide as realistically as possible by imagining that the monetary reward is actually available for choice.

@@

Data collection and analysis will not be performed blind to the conditions of the experiments.
Data of whole participants will be excluded from analysis if participants withdraw their consent or they state that they did not follow experimental instructions.
EMG data of subjects will be excluded from analysis if errors occured during recording.
No further data exclusions are planned.
The level of significance will be set to $\alpha=.05$.
For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the *afex* package[@Singmann2021].
Greenhouse-Geisser-corrected degrees of freedom and associated $p$-values will be reported when the assumption of sphericity is violated.
If the within-subjects factor of interest is significant, pairwise contrasts will be calculated using Bonferroni adjustment for multiple testing.
Proportion of explained variance $\eta_{p}^{2}$ will be reported as a measure of effect size.

@@

*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.02 € will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy will be divided by 2 €.
Therefore, the SVs of the flexible strategies are 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they are the preferred strategy of each pairing.
The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing. 
The final SV per strategy for each participant will be computed by averaging the SVs of each strategy across pairings.
